Figure 3. Tissue Microbiome Abundances

### 2023-03-08 reports/manuscript/Figure3.Rmd
show code in output document

```{r Figure 3, echo=FALSE, warning=FALSE, message=FALSE, fig.pos="t"}
# fig.asp=1, fig.height=7,
### A
#############################
# DIVERSITY + TAX ABUNDANCE #
#############################
figlabels <- letters

>>>>

```{r Figure 3, warning=FALSE, message=FALSE, fig.pos="t"}
# fig.asp=1, fig.height=7,
### A
#############################
# DIVERSITY + TAX ABUNDANCE #
#############################
figlabels <- letters
